Bayesian determination of the effect of a deep eutectic solvent on the structure of lipid monolayers

### 2018-10-17 reports/preprint.tex
fix reference for des roughness

For each lipid, the tail layer thickness, $d_t$, increases with chain length and in general agrees with the literature for monolayers on water\cite{Mohwald1990,Vaknin1991}:
For DMPC, \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water, and for DPPC \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water.
In all cases the surface roughness was found to be relatively high compared to water. This is expected because the absolute surface tension of the DES is less than water\cite{Arnold2015}.

>>>>

For each lipid, the tail layer thickness, $d_t$, increases with chain length and in general agrees with the literature for monolayers on water\cite{Mohwald1990,Vaknin1991}:
For DMPC, \input{../output/dmpc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{15.8}{\angstrom}$ at \SI{30}{\milli\newton\per\meter}\cite{Johnson1991} in water, and for DPPC \input{../output/dppc/tail30.txt}\si{\angstrom} at \SI{30}{\milli\newton\per\meter} in DES compared with $d_t=\SI{16.7}{\angstrom}$ at \SI{40}{\milli\newton\per\meter}\cite{Helm1987} in water.
In all cases the surface roughness was found to be relatively high compared to water.
This is expected because the absolute surface tension of the DES is less than water, while a previous XRR measurement of pure choline chloride:glycerol suggests a roughness of 3.3\si{\angstrom}\cite{Sanchez-Fernandez2016}, significantly higher than the capillary wave roughness of water of about 2.8\si{\angstrom}.
